---
title: "Assignment1 Part 2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2. KM estimates of IMRAW-IST data

```{r read data}
library(survival)
IMRAWIST = data.frame(readxl::read_excel("IMRAWandISTnov.xls"))
IMRAWIST$AMLorDIED = sapply(1:nrow(IMRAWIST), 
                            function(k) max(IMRAWIST$AML[k], IMRAWIST$DIED[k]))
IMRAWIST$AMLorDIED_TIME = sapply(1:nrow(IMRAWIST), 
                                 function(k) min(IMRAWIST$AMLTIME[k], IMRAWIST$survival[k]))
```

### 2.1 Calculate the KM estimate and its 95% pointwise confidence interval of $S(t)$ for time to death of the IST patients.

```{r}
IST_DEATH = survfit(Surv(time = survival, event = DIED) ~ 1, 
                    type = "kaplan-meier",
                    data = IMRAWIST, subset = (NIH==1))
plot(IST_DEATH, main = "KM estimate of IST patients for time to death")
```


### 2.2 Calculate the KM estimate and its 95% pointwise confidence interval of $S(t)$ for timeto AML or death of the IST patients.

```{r}
IST_DEATH_AMLorDIED = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                              type = "kaplan-meier",
                              data = IMRAWIST, subset = (NIH==1))
plot(IST_DEATH_AMLorDIED, main = "KM estimate of IST patients for time to AML or death")
```

### 2.3 Repeat (2.1) and (2.2) for men and women separately.

#### Men

```{r}
IST_DEATH_Men = survfit(Surv(time = survival, event = DIED) ~ 1, 
                        type = "kaplan-meier",
                        data = IMRAWIST, subset = (NIH==1 & GENDER=="M"))
plot(IST_DEATH_Men, main = "KM estimate of male IST patients for time to death")

IST_DEATH_AMLorDIED_Men = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                                  type = "kaplan-meier",
                                  data = IMRAWIST, subset = (NIH==1 & GENDER=="M"))
plot(IST_DEATH_AMLorDIED_Men, main = "KM estimate of male IST patients for time to AML or death")
```

#### Women

```{r}
IST_DEATH_Women = survfit(Surv(time = survival, event = DIED) ~ 1, 
                          type = "kaplan-meier",
                          data = IMRAWIST, subset = (NIH==1 & GENDER=="F"))
plot(IST_DEATH_Women, main = "KM estimate of female IST patients for time to death")

IST_DEATH_AMLorDIED_Women = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                                    type = "kaplan-meier",
                                    data = IMRAWIST, subset = (NIH==1 & GENDER=="F"))
plot(IST_DEATH_AMLorDIED_Women, main = "KM estimate of female IST patients for time to AML or death")
```

### 2.4 Repeat (2.1) and (2.2) for patients with “IPSS high” and not “IPSS high” separately.

#### IPSS high

```{r}
IST_DEATH_IPSShigh = survfit(Surv(time = survival, event = DIED) ~ 1, 
                             type = "kaplan-meier",
                             data = IMRAWIST, subset = (NIH==1 & IPSS=="High"))
plot(IST_DEATH_IPSShigh, 
     main = "KM estimate of IST patients with high IPSS for time to death")

IST_DEATH_AMLorDIED_IPSShigh = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                                       type = "kaplan-meier",
                                       data = IMRAWIST, subset = (NIH==1 & IPSS=="High"))
plot(IST_DEATH_AMLorDIED_IPSShigh, 
     main = "KM estimate of IST patients with high IPSS for time to AML or death")
```

#### IPSS not high

```{r}
IST_DEATH_IPSSnothigh = survfit(Surv(time = survival, event = DIED) ~ 1, 
                                type = "kaplan-meier",
                                data = IMRAWIST, subset = (NIH==1 & IPSS!="High"))
plot(IST_DEATH_IPSSnothigh, 
     main = "KM estimate of IST patients without high IPSS for time to death")

IST_DEATH_AMLorDIED_IPSSnothigh = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                                          type = "kaplan-meier",
                                          data = IMRAWIST, subset = (NIH==1 & IPSS!="High"))
plot(IST_DEATH_AMLorDIED_IPSSnothigh, 
     main = "KM estimate of IST patients without high IPSS for time to AML or death")
```

### 2.5 Calculate the KM estimate and its 95% pointwise confidence interval of $S(t)$ for time to death of the IMRAW patients.

```{r}
IMRAW_DEATH = survfit(Surv(time = survival, event = DIED) ~ 1, 
                      type = "kaplan-meier",
                      data = IMRAWIST, subset = (NIH==0))
plot(IMRAW_DEATH, main = "KM estimate of IMRAW patients for time to death")
```

### 2.6  Calculate the KM estimate and its 95% pointwise confidence interval of $S(t)$ for timeto AML or death of the IMRAW patients.

```{r}
IMRAW_DEATH_AMLorDIED = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                                type = "kaplan-meier",
                                data = IMRAWIST, subset = (NIH==0))
plot(IMRAW_DEATH_AMLorDIED, main = "KM estimate of IMRAW patients for time to AML or death")
```

### 2.7 Repeat (2.5) and (2.6) for men and women separately.

#### Men

```{r}
IMRAW_DEATH_Men = survfit(Surv(time = survival, event = DIED) ~ 1, 
                          type = "kaplan-meier",
                          data = IMRAWIST, subset = (NIH==0 & GENDER=="M"))
plot(IMRAW_DEATH_Men, main = "KM estimate of male IMRAW patients for time to death")

IMRAW_DEATH_AMLorDIED_Men = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                                    type = "kaplan-meier",
                                    data = IMRAWIST, subset = (NIH==0 & GENDER=="M"))
plot(IMRAW_DEATH_AMLorDIED_Men, 
     main = "KM estimate of male IMRAW patients for time to AML or death")
```

#### Women

```{r}
IMRAW_DEATH_Women = survfit(Surv(time = survival, event = DIED) ~ 1, 
                            type = "kaplan-meier",
                            data = IMRAWIST, subset = (NIH==0 & GENDER=="F"))
plot(IMRAW_DEATH_Women, 
     main = "KM estimate of female IMRAW patients for time to death")

IMRAW_DEATH_AMLorDIED_Women = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                                      type = "kaplan-meier",
                                      data = IMRAWIST, subset = (NIH==0 & GENDER=="F"))
plot(IMRAW_DEATH_AMLorDIED_Women, 
     main = "KM estimate of female IMRAW patients for time to AML or death")
```

### 2.8 Repeat (2.5) and (2.6) for patients with “IPSS high” and not “IPSS high” separately.

#### IPSS high

```{r}
IMRAW_DEATH_IPSShigh = survfit(Surv(time = survival, event = DIED) ~ 1, 
                               type = "kaplan-meier",
                               data = IMRAWIST, subset = (NIH==0 & IPSS=="High"))
plot(IMRAW_DEATH_IPSShigh, 
     main = "KM estimate of IMRAW patients with high IPSS for time to death")

IMRAW_DEATH_AMLorDIED_IPSShigh = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                                         type = "kaplan-meier",
                                         data = IMRAWIST, subset = (NIH==0 & IPSS=="High"))
plot(IMRAW_DEATH_AMLorDIED_IPSShigh, 
     main = "KM estimate of IMRAW patients with high IPSS for time to AML or death")
```

#### IPSS not high

```{r}
IMRAW_DEATH_IPSSnothigh = survfit(Surv(time = survival, event = DIED) ~ 1, 
                                  type = "kaplan-meier",
                                  data = IMRAWIST, subset = (NIH==0 & IPSS!="High"))
plot(IMRAW_DEATH_IPSSnothigh, 
     main = "KM estimate of IMRAW patients without high IPSS for time to death")

IMRAW_DEATH_AMLorDIED_IPSSnothigh = survfit(Surv(time = AMLorDIED_TIME, event = AMLorDIED) ~ 1, 
                                            type = "kaplan-meier",
                                            data = IMRAWIST, subset = (NIH==0 & IPSS!="High"))
plot(IMRAW_DEATH_AMLorDIED_IPSSnothigh, 
     main = "KM estimate of IMRAW patients without high IPSS for time to AML or death")
```
